Digital History in Finland, 1488-1828

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

>>>>

### Finland in the Swedish context

- Dramatic events regarding the diversity of "Finnishness" take place in the early nineteenth century --- but the analysis of Finnish knowledge production 1828-2016 is for another day.

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
df <- subset(df0, catalog == "Fennica") %>%
  filter(publication_year >= 1640 & publication_year <= 1800)%>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity", color = "black") +
     ggtitle("Title count") +
     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     scale_fill_grey() +
     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
     xlab("Publication decade") + ylab("Title count (n)")
print(p)
```
---
